An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-15 paper/paper.tex
Paper: small fixes

% TODO cite router.bittorrent.com as well known bootstrap node?
%In BitTorrent's structured overlay network \footnote{To clarify, we are referring to BitTorrent's distributed hash table, not its unstructured network. The latter involves using centralized trackers, the former removes such dependency. We refraim from using the term \textit{distributed hash table} to keep the explanation simple without loss of generality. We discuss distributed hash tables in section \ref{sec:backgroundDHT}.}, a well known bootstrap node \footnote{The BitTorrent specification uses \textit{node} to refer to participants of its structured overlay network and \textit{peer} as a more general term \cite{bittorrentDHT}. We will adopt this convention when speaking about BitTorrent, and use them interchangeably otherwise.} is router.bittorrent.com. A BitTorrent node randomly chooses a 160 bit \textit{nodeID} to use as an address. To join the network, it will contact a bootstrap node to find the nodes it is closest to in the topology. Closeness, in BitTorrent's case, is determined by taking the $XOR$ of \textit{nodeID}s; smaller values are defined as closer \cite{bittorrentDHT}.
% TODO define XOR?
% TODO maybe remove this entire paragraph, since it doesn't really clarify anything. it just gives another example of picking an id and mysteriously finding nodes its closest to. if we end up remove it, we should reword end of previous paragraph

@@

For every file a peer wishes to back up, it must find a predetermined number of nodes that can store the file. To ensure an even distributionof responsibility in the structured overlay network, a random bitstring in the address space of the overlay network is generated. The DHT provides the functionality to find the node whose ID is \textit{closest} to the randomly generated bitstring. The peer then gets the metadata record for the node from the DHT. From the metadata record, the peer can calculate if the node is \textit{obligated} to store its file. We discuss the situation in which a node is obligated to store a peers file in section \ref{sec:Fairness}. The peer also uses the metadata record to ensure the node does not have too many blacklisters. If the node meets both requirements, the peer uses the data layer to contact the node to inform it of the decision. The metadata layer is updated appropriately, and the data layer is used to transfer the file. This process repeats until the predetermined number of nodes are found.

>>>>

% TODO cite router.bittorrent.com as well known bootstrap node?
%In BitTorrent's structured overlay network \footnote{To clarify, we are referring to BitTorrent's distributed hash table, not its unstructured network. The latter involves using centralized trackers, the former removes such dependency. We refraim from using the term \textit{distributed hash table} to keep the explanation simple without loss of generality. We discuss distributed hash tables in section \ref{sec:backgroundDHT}.}, a well known bootstrap node \footnote{The BitTorrent specification uses \textit{node} to refer to participants of its structured overlay network and \textit{peer} as a more general term \cite{bittorrentDHT}. We will adopt this convention when speaking about BitTorrent, and use them interchangeably otherwise.} is router.bittorrent.com. A BitTorrent node randomly chooses a 160 bit \textit{nodeID} to use as an address. To join the network, it will contact a bootstrap node to find the nodes it is closest to in the topology. Closeness, in BitTorrent's case, is determined by taking the $XOR$ of \textit{nodeID}s; smaller values are defined as closer \cite{bittorrentDHT}.
% TODO define XOR?
% TODO maybe remove this entire paragraph, since it doesn't really clarify anything. it just gives another example of picking an id and mysteriously finding nodes its closest to. if we end up remove it, we should reword end of previous paragraph
% TODO maybe keep it in b/c we refer to closness in 3.1.1

@@

For every file a peer wishes to back up, it must find a predetermined number of nodes that can store the file. To ensure an even distribution of responsibility in the structured overlay network, a random bitstring in the address space of the overlay network is generated; the DHT provides the functionality to find the node whose ID is \textit{closest} to the randomly generated bitstring, for the overlay network's given definition of closeness. The peer then gets the metadata record for the candidate node from the DHT. From the metadata record, the peer can calculate if the candidate node is \textit{obligated} to store its file. We discuss the situation in which a node is obligated to store a peers file in section \ref{sec:Fairness}. The peer also uses the metadata record to ensure the candidate node does not have too many blacklisters. If the candidate node meets both requirements, the peer chooses it to store a replica and uses the data layer to contact the node to inform it of the decision. The metadata layer is updated appropriately, and the data layer is used to transfer the file. This process repeats until the predetermined number of nodes are found.
